QPLIB: A Library of Quadratic Programming Instances

### 2018-02-05 AnswerToTheReferees.tex

{\it
I have received two reviews for this manuscript, and while there is consensus that the library makes an important contribution, one of the reviewers in particular had significant concerns with the library and the manuscript describing it. The most significant concern, which I share, is that the paper is significantly longer than it needs to be. In particular, I did not see a great need to review the solution methods as is done in Section 2.3. Mentioning the current solvers, and which classes of problems they can solve according to your taxonomy is perhaps useful for a reader's reference. But attempting to describe the algorithms themselves is somewhat futile, as it takes significant space and yet is still an inadequate description. For that, it would be better to simply provide some references for the benefit of readers who are interested in understanding the algorithms in the solvers. 
}

\rep{We agree with the AE that the description of the solution methods goes beyond the scope of the paper. For this reason we have streamlined Section 2.3 which now contains only a quick overview of the solvers and their solution methods. 
%\leo{Togliamo la spiegazione degli algoritmi e sostituiamola con una citazione di un book-tutorial-survey-introduction.}
}

{\it
I also agree with the reviewer's concern that some of the instance classes have only a single instance in them. If I am a researcher designing a method for solving instances in that class, I will be pretty disappointed to find that QPLIB only has a single relevant test instance. 
}

\rep{
We performed an internal call for instances among the members of the committee. 
We gathered $86$ new instances (belonging to the categories less that were not well represented) and we added them to the library. We added a macro classification of the instances, based on convexity and nature of the variables.
We believe that the majority of the algorithms used in the literature falls in one of these categories.
This macro classification shows that the library is now well-balanced.
We kept also the detailed classification since it allows a fine grained analysis of the instances.
%%
%\leo{Sono d'accordo, ma come/dove troviamo le istanze supplementari? Sono le categorie con  $<10$ istanze nelle tavole 4 e 5, giusto? Dire che ce ne sono parecchie. 15 categorie su 23 hanno meno di 10 istanze (il numero 10 e` magico perche' le nostre mani hanno dieci dita, ovviamente).} 
}

@@

\end{enumerate}
}

\subsection*{Point-by-point reply to the Referee 2}

{\it
The paper presents a library of quadratic programming (QP) instances, where QP is broadly interpreted
to include quadratically constrained, and integer programs too. While I appreciate the overall goal of
the project, the paper is poorly written. It is often long-winded, and contains numerous factual errors,
and some omissions that must be corrected. Overall, the paper can easily be cut by 5-10 pages.
}

\rep{We followed the suggestion of the referee and the AE and we have shortened unnecessary sections of the paper.}

@@

{\it
\begin{enumerate}

\item There are two classes of important missing application domains of QPs in Table 1: (1) trust-region subproblems, and (2) PDE-constrained optimization problems. In fact, there exist a number of PDE-constrained instances in CUTEr, which would be useful additions to the library. The authors should add at least a few such examples. the lack of these problems is worrying, because
it (implicitly) assumes that direct solvers are used, which means that this library is less relevant for matrix-free solvers.

\rep{
Thank you for pointing out the missing categories. As requested, we updated Table 1 with the two required applications.
We also included PDE-constrained instances in the updated version of the library.
We have deliberately excluded the highly-specialized class of trust-region subproblems, since there are dedicated, very fast solvers for this class. See for example:
\begin{itemize}
\item
Minimizing a quadratic over a sphere. \\
W. W. Hager. 
SIAM Journal on Optimization,12(1):188-208, 2001.
\item
Solving the trust-region subproblem using the Lanczos method. \\
N. I. M. Gould, S. Lucidi, M. Roma, and Ph. L. Toint. 
SIAM Journal on Optimization, 9(2):504-525, 1999.
\item
A semidefinite framework for trust region subproblems with applications to large scale minimization.\\
F Rendl, H Wolkowicz.
Mathematical Programming 77 (1), 273-299
\item
A Subspace Minimization Method for the Trust-Region Step.\\
J. B. Erway and P. E. Gill.
SIAM J. Optim. 20-3 (2010), pp. 1439-1461
\item
Solving the Trust-Region Subproblem By a Generalized Eigenvalue Problem.\\
S. Adachi, S. Iwata, Y. Nakatsukasa and A Takeda.
SIAM Journal on Optimization 27 (1), 269-291
\item
On solving trust-region and other regularised subproblems in optimization.\\
N.I.M. Gould, D.P. Robinson and H.S. Thorne.
Mathematical Programming Computation 2 (1), 21-57
\end{itemize}
%\leo{sono d'accordo, dovremmo aggiungere delle istanze da trust-region subproblem e delle istanze da problemi PDE-constrained. Chiediamo a Gould per le istanze trust-region e a Gould, Mittelmann e Sahinidis per PDE-constrained. Specifichiamo che vorremmo istanze NON gia` in CUTE.} 
}

@@

\item The description of NLP solvers in Section 2.3.2 is at somewhat misleading. For example, KNITRO is also a primal-dual interior-point method, not just a barrier code (in fact primal-dual
methods are preferred). The description of the “active-set” methods is wrong, unless you refer
to the inner method, namely the active-set QP solves. Otherwise, SNOPT and KNITRO are
SQP methods, while CONOPT is a gradient-projection method, and MINOS is an augmented
Lagrangian method. You must correct this section

\rep{The complete description of the solver goes beyond the scope of the paper. For this reason we have streamlined the related Section.
%\leo{correggiamo gli errori e ringraziamo il referee} 
}

\item Some classes of problems in Table 4 do not seem to have many instances. Please create more.

\rep{We followed your suggestion and we gathered several additional instances which we included in the final version of the library (see the reply to the AE for further details).}

### 2018-02-05 QPLIB-1.0.tex
Update QPLIB-1.0.tex

A consequence of our focus is that this paper is \emph{not} concerned with the performance of the very diverse available set of QP solvers; we will \emph{not} report any data comparing them. The only reason that solvers are used (and, therefore, described) in this context is to ensure that the instances of the library are nontrivial---at least for a significant fraction of the current solution methods. Providing guidance about which solvers are most suited to some specific class of QPs is entirely outside the scope of our work.

@@

In addition, QP, with continuous or integer variables, is arguably a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many optimization problems \cite{Kochenberger2014}. Table \ref{tbl:application} provides a certainly non-exhaustive collection of applications that lead to formulations with quadratic constraints, quadratic objective function, or both. In general, any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree. In turn, every polynomial can be broken down to a system of quadratic expressions. Hence, QP is, in some sense, roughly as expressive as MINLP. This is, in principle, true for MILP as well, but at the cost of much larger and much more complicated formulations. Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of MILP and the higher expressive power, but much higher computational cost of MINLP.

>>>>

A consequence of our focus is that this paper is \emph{not} concerned with the performance of the very diverse available set of QP solvers; we will \emph{not} report any data comparing them. The only reason that solvers are used (and, therefore, described) in this context is to ensure that the instances of the library are nontrivial, at least for a significant fraction of the current solution methods. Providing guidance about which solvers are most suited to some specific class of QPs is entirely outside the scope of our work.

@@

In addition, QP, with continuous or integer variables, is arguably a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many optimization problems \cite{Kochenberger2014}. Table \ref{tbl:application} provides a certainly non-exhaustive collection of applications that lead to formulations with quadratic constraints, quadratic objective function, or both. In general, any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree. In turn, every polynomial can be broken down to a system of quadratic expressions. Hence, QP is, in some sense, roughly as expressive as MINLP. This is, in principle, true for MILP as well, but at the cost of much larger and much more complicated formulations. Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of MILP and the higher expressive power, but much higher computational cost, of MINLP.
